---
name: Jake
surname: Riley
position: "Senior Data Analyst | Philadelphia, PA"
phone: 202-243-9677
#www: xyz.com
email: "rjake@sas.upenn.edu"
#twitter: xyz
github: rjake
#linkedin: xyz
headcolor:  "333333" # "3E7474" # simplecolors::sc("dullteal4")
date: "`r format(Sys.time(), '%B %Y')`"
#aboutme: "I have been working with data since 2003. I have a deep passion for automation, collaboration, and advancing data literacy. This resume was even compiled with code. My work history is interwoven with school and working for social service organizations; this is resume reflects the most relevant work history in my analytics career."

output: 
    vitae::awesomecv:
      keep_tex: true
      #latex_engine: xelatex # may need to run tinytex::install_tinytex()
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(vitae)
library(tidyverse)
library(glue)
library(rlang)
library(fontawesome)

list_to_entry <- function(x) {
  df <- purrr::map_dfr(x, as_tibble)
  f <- detailed_entries #partial(detailed_entries, .protect = FALSE)
  
  # rearrange formals
  formal_names <- names(formals(f))
  
  explicit_args <- 
    match(
      c("data", names(df)),
      formal_names
    )
    
  missing_args <- setdiff(seq_along(formal_names), explicit_args)
  
  formals(f) <- formals(f)[c(explicit_args, missing_args)]

  # make expr
  expr(f(df, !!!parse_exprs(names(df)))) |> 
    eval()
}


```

# \faIcon{briefcase} Relevant Work Experience

```{r}
list(
  list(
    with = "Clinical Data Programmer / Analyst III",
    what = "Children's Hospital of Philadelphia",
    when = "2017 - Present",
    where = "Philadelphia, PA",
    why = c(
      "\textbf{Mentor} and accelerate technical capital of analytics team while reducing technical debt",
      "Innovate and enhance in-house data solutions (R packages, dashboard templates, trusted data layer)",
      #"Analytics pipeline from query (SQL) to dashboards and reporting",
      "Consult on analytic strategy, data visualization, and technical solutions", 
      #"Developed automated query generation methodology for US News (~1000 questions)",
      "Introduce novel datasets to our data warehouse (ex. diagnosis hierarchy, self-generating calendars)",
      "Built data infrastructure that became foundation for enterprise tables",
      "Tools: SQL, Qliksense, dbt, R, shiny, VS Code"
    )
  ),
  list(
    with = "BI Analyst - Human Resources",
    what = "Comcast",
    when = "2016 - 2017",
    where = "Philadelphia, PA",
    why = c(
      "Built new dashboards for employee turnover, data dictionary, and underrepresented minorities for up to 1,200 end users", 
      "Automated a quarterly report for the senior vice president of human resources",
      "Helped peers use the right methods to generate insights and visualize results",
      "Provided difficult analyses such as travelling salesman problems",
      "Tools: SAP Business Objects, Tableau, R"
    )
  ),
  list(
    with = "Data Analyst",
    what = "PolicyMap",
    when = "2015 - 2016",
    where = "Philadelphia, PA",
    why = c(
      "Aggregated over 150 national datasets across 9 geographies", 
      "Developed new automated process for testing and data validation",
      "Tools: SQL, ArcMap, R"
    )
  ),
  list(
    with = "Production Analyst",
    what = "Whole Foods Market",
    when = "2003 - 2008",
    where = "Landover, MD",
    why = c(
      "Responsible for automating the production schedule for the Mid-Atlantic commissary", 
      "Determined ingredient quantity for daily and holiday orders of 32 stores", 
      "Minimized redundant usage of kitchen equipment (only want to prep and clean each station once)",
      "Determined how many 180-gallon kettles of soup to be made each hour",
      "Tools: Excel/VBA"
    )
  )
) |> 
  list_to_entry()

```

# \faIcon{university} Education

```{r}
list(
  list(
    with = "University of Pennsylvania",
    what = "B.A. Sociology - Quantitative Methods  |  summa cum laude  |  phi beta kappa",
    when = "2012-2015",
    where = "Philadelphia, PA",
    why = "Non-traditional student. Coursework focused on data analysis, GIS, and data visualization. Projects focused on census data and demography."
  ),
  list(
    with = "Community College of Philadelphia",
    what = "A.A. Liberal Arts | with highest honors | phi theta kappa",
    when = "2011-2012",
    where = "Philadelphia, PA",
    why = NA_character_
  )#,
  # list(
  #   with = "Montgomery County Community College",
  #   what = "part-time general studies",
  #   when = "2003-2005",
  #   where = "Rockville, MD",
  #   why = NA_character_
  # )
) |> 
  list_to_entry()
```

# \faIcon{cogs} Skills

```{r eval=F}
library(kableExtra)

list(
  `highly proficient` = c("data manipulation", "data viz", "tidyverse", "package dev", "code review"),
  proficient = c("SQL", "Tableau", "Qliksense", "shiny", "GitHub", "GIS", "demography"),
  novice = c("JavaScript", "CSS", "DBT", "APIs"),
  interested = c("Python", "Machine Learning", "Statistics")
) |>
  map(sort) |>
  map(glue_collapse, " -- ") |>
  flatten_df() |>
  kable(booktabs = TRUE, align = "c", escape = FALSE, format = "latex") |>
  # kable(booktabs = TRUE, align = "c") |>
  kable_styling(full_width = F, font_size = 9) |>
  row_spec(0, bold = T, color = "#009acd") |>
  row_spec(1, bold = F, color = "#7f7f7f") |>
  column_spec(column = 1:4, width = "4.75cm")

#knitr::knit_exit()
```


\footnotesize

* **highly proficient** data manipulation & visualization -- tidyverse -- package development -- code review 
* **proficient** sql -- tableau -- qliksense -- shiny -- github -- gis -- census data
* **novice** javascript -- css -- dbt -- api
* **interested** python -- machine learning -- advanced statistics


# \faIcon{laptop-code} R Packages

* **headliner** *(author)* generates building blocks for creating dynamic text \href{https://rjake.github.io/headliner/}{\tiny\color{lightgray}\faLink} 
* **shinyobjects** *(author)* allows the user to debug reactive objects interactively \href{https://rjake.github.io/shinyobjects/index.html}{\tiny\color{lightgray}\faLink}
* **simplecolors** *(author)* a simple color palette that is intuitive and easy to remember   \href{https://rjake.github.io/simplecolors/articles/intro.html}{\tiny\color{lightgray}\faLink} 
* **whereiation** *(author)* where(is the var)iation - an automated exploratory data analytics pacakage \href{https://rjake.github.io/whereiation/}{\tiny\color{lightgray}\faLink} 


```{r}
knitr::knit_exit()
```

# \faIcon{users} Volunteer/Community

**Philadelphia, PA** Code for Philly (contributor), Compass (data), Iraq Veterans Against the War (data), #MakeoverMonday (tableau), Men’s Resource Center (facilitator), Mill Creek Farm (data), Neighborhood Bike Works (facilitator), OpenDataPhilly (data), Project HOME (data), R-Ladies (speaker), TechCamp Philly (data), TransHealth Conference (data)

**Washington, DC** DC Trans Coalition (advocate), Emergence Community Arts Collective (data), OneDC (data)


# Examples:
https://github.com/tallguyjenks/CV/blob/master/CV.pdf
https://github.com/akirosingh/CV/blob/master/CV.pdf
https://github.com/mlampros/My.CVitae/blob/master/docs/cv.pdf
https://github.com/loreabad6/R-CV/blob/master/CV.pdf
https://github.com/jooyoungseo/jy_CV/blob/master/docs/JooYoung_Seo_Short_CV.pdf
https://github.com/seabbs/cv/blob/master/cv/cv.pdf

Can open like this??? https://docs.google.com/viewer?url=https://raw.githubusercontent.com/loreabad6/R-CV/master/CV.pdf
