---
title: "Introduction to Modern Statistics"
output: html_document
date: "2022-11-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*Authors - Mine Çetinkaya-Rundel and Johanna Hardin*

<<<<<<< Updated upstream
* Site - https://openintro-ims.netlify.app/index.html
* Repo - https://github.com/openintrostat/ims

* Tutorials - https://openintrostat.github.io/ims-tutorials/
* Labs - http://openintrostat.github.io/oilabs-tidy/
=======
-   Site - <https://openintro-ims.netlify.app/index.html>

-   Repo - <https://github.com/openintrostat/ims>

-   Tutorials - <https://openintrostat.github.io/ims-tutorials/>

-   Labs - <http://openintrostat.github.io/oilabs-tidy/>
>>>>>>> Stashed changes

```{r workspace}
library(openintro)
library(tidyverse)
```

<<<<<<< Updated upstream
## Chapter 1

### Stents
Does the use of stents reduce the risk of stroke?

```{r}
stent30
stent365

```

## Chapter 2
```{r}

```

## Chapter 3
=======
## Chapter 2

- **census** = entire population
- **sample** = subset of population
- **parameter** = summary measurement for population
- **statistic** = summary measurement for sample

```{r}
UCBAdmissions |>
  as.data.frame() |> 
  count(Dept, Gender, Admit, wt = Freq) |> 
  group_by(Dept, Gender) |> 
  summarise(pct = sum(n[Admit == "Admitted"]) / sum(n)) |> 
  ungroup() |> 
  spread(Gender, pct)

#  Dept    Male  Female
# 
#  A     0.621   0.824  TRUE 
#  B     0.630   0.68   TRUE
#  C     0.369   0.341  FALSE
#  D     0.331   0.349  TRUE
#  E     0.277   0.239  FALSE
#  F     0.0590  0.0704
  
ucb_admit %>%
  # Group by department, then gender
  group_by(Dept, Gender) %>%
  # Table of counts of admission status and gender and department
  count(Admit) %>%
  # Create new variable
  mutate(prop = n / sum(n)) 
```

## Chapter 3

>>>>>>> Stashed changes
```{r}

```

## Chapter 4
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 5
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 6
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 7
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 8
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 9
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 10
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 11
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 12
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 13
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 14
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 15
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 16
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 17
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 18
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 19
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 20
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 21
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 22
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 23
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 24
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 25
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 26
<<<<<<< Updated upstream
=======

>>>>>>> Stashed changes
```{r}

```

## Chapter 27
<<<<<<< Updated upstream
```{r}

```

=======

```{r}

```
>>>>>>> Stashed changes
