---
title: "Cirlce Packing"
author: "Jake"
date: "October 5, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#inspiration
[circlism](http://cse.iitkgp.ac.in/~pb/research/circlism/)
[google](https://www.google.com/search?q=digital+circlism)
[stackoverflow](https://mathematica.stackexchange.com/questions/40334/generating-visually-pleasing-circle-packs)
[Mitchell's Best-Candidate](https://bl.ocks.org/mbostock/1893974)
[fill svg shape](https://bl.ocks.org/gouldingken/8d0b7a05b0b0156da3b8)
[Voroni + tirangulation](https://www.researchgate.net/figure/273284325_fig7_Figure-7-An-example-of-a-Voronoi-diagram-in-Laguerre-geometry-for-a-set-of-multi-sized)
[inspiration](https://gravyanecdote.com/uncategorized/making-the-kraken-part-1-getting-the-image-and-data/)


#workspace
*to plot ```ggeom_sf()``` the dev version of ```ggplot``` must be used. More detail can be found [here](http://strimas.com/r/tidy-sf/)
```{r}
#library(devtools)
#devtools::install_github("tidyverse/ggplot2", force = T)
#devtools::install_github("sjp/grImport2")
#library(alphahull) #for optimized convex hulls
#library(ConR) #alpha hulls for clustering points
#library(doParallel)
#library(foreach)
library(imager)
library(maptools)
library(raster)
library(sf)
library(tidyverse)

options(warn = -1)
options(scipen = 999)

setwd("C:/Users/Public/Pictures")
#library(svglite)
#library(grImport2)
#library(png)

image_file <- "kraken.png"

```

```{r}
#imager
#plot(boats)
#plot(load.image("starrynight.png"))
#plot(load.image("gears.png"))
#plot(load.image("fish_perch.png"))
#plot(load.image("orca.png"))
#plot(load.image("emma_sm.png"))
#plot(load.image("kraken.png"))
#plot(load.image(image_file))

modulo <- 2
blur_amt <- 3000

plot(blur_anisotropic(load.image(image_file), 
                      amplitude = blur_amt))

image_initial <-
  blur_anisotropic(load.image(image_file), amplitude = blur_amt) %>% 
  #load.image(image_file) %>% 
  as.data.frame() %>% 
  #filter(#y < 90, 
  #       x > 90) %>%
  tidyr::spread(key = cc, value = value) %>%
  rename(r = `1`,
         g = `2`,
         b = `3`) %>% 
#  set_names(c("x", "y", "r", "g", "b", "a")) %>% #may need to remove "a" 
  mutate_all(as.numeric) %>% 
  filter((x %% modulo == 0 & y %% modulo == 0) |
         (x %% modulo == (modulo/2) & y %% modulo == (modulo/2))) %>% 
  mutate(y = -y)

grid_base <-
  image_initial %>% 
  mutate(hex = rgb(r, g, b, maxColorValue = 1)) %>% 
  rowwise() %>% 
  mutate(h = rgb2hsv(r, g, b, maxColorValue = 1)[[1]][1],
         s = rgb2hsv(r, g, b, maxColorValue = 1)[[2]][1],
         v = rgb2hsv(r, g, b, maxColorValue = 1)[[3]][1]) %>%
  ungroup() %>% 
  mutate(h2 = round(h/.1) * .1, #0.05
         s2 = .5, #round(s/.33)*.33,
         v2 = round(v/.33)*.33,
         hex2 = hsv(h2, s2, v2))

n_distinct(grid_base$hex2)

ggplot(grid_base, aes(x, y, color = hex2)) +
  geom_point(size = 3) +
  #scale_y_reverse() +
  guides(color = F) +
  coord_fixed() +
  scale_color_identity() +
  theme_bw()

ggplot(grid_base, aes(x, y, color = hex2)) +
  geom_point() +
  scale_color_identity() +
  facet_wrap(~hex2, nrow = 4) +
  theme_minimal() +
  theme(panel.grid = element_blank(),
        axis.text = element_blank(),
        panel.border = element_rect(color = "grey40", fill = NA))
```

### NEW METHOD - concave hulls ######################
```{r}
#create convex hulls
color_points <- 
  grid_base %>% 
  st_as_sf(coords = c("x", "y")) %>% 
  select(hex, h2, s2, v2, hex2) %>% 
  mutate(area = 1) %>% 
  st_buffer(dist = modulo * 0.6, nQuadSegs = 4)

ggplot(color_points) +
  geom_sf(aes(fill = hex2), alpha = .8) +
  scale_fill_identity()

color_clusters <-
  color_points %>% 
  select(hex2) %>% 
  group_by(hex2) %>% 
  summarize() %>% 
  ungroup() %>% 
  st_cast() %>% 
  st_cast("POLYGON") %>% 
  st_simplify(dTolerance = 1)  %>% 
  mutate(area = st_area(.)) %>% 
  arrange(area) %>% 
  st_buffer(0.5)

ggplot(color_clusters) +
  geom_sf(aes(fill = hex2), alpha = .8) +
  scale_fill_identity()
```




# for loop
```{r}
  color_circle_all <-
    color_clusters %>%
    slice(0)

  area_allowed <- floor(min(color_clusters$area))
  
  buffer_min <- sqrt(area_allowed)/pi

  get_iteration <- 1   


#LOOP  
system.time(
for(i in 1:NROW(color_clusters)){
  #plot(color_polygon$geometry, col = color_polygon$hex2, add = F)
  
  color_polygon <-
    color_clusters %>%     
    slice(i) %>% 
    st_difference(st_union(color_circle_all)) %>% 
    filter(area > area_allowed)

  #plot(color_clusters$geometry, col = NA, add = F)
    #plot(color_circle_all$geometry, col = "red", add = T)
      #plot(color_polygon$geometry, col = color_polygon$hex2, add = F)

    j = 1
  
  area_left = T
  rows_left = NROW(color_polygon)

  while(area_left == T || rows_left == 1){
    if(area_left != T && rows_left > 1){
      #drop current row and go to next row
          color_polygon <-
              color_polygon %>% 
              slice(-1)
          
          print("try next row")
          next()
    } 
    else {
      #update variable values    
        get_area <- color_polygon$area[1]
        rows_left <- nrow(color_polygon)
        area_left <- get_area > area_allowed
      
      #take the first row from the data  
        color_polygon_single <-
          color_polygon %>% 
          slice(1)
        
      #check to see if the buffer leaves enough space to plot
        color_buffer <-
          color_polygon_single %>% 
          st_buffer(-buffer_min) %>% 
          mutate(area = st_area(.))
        
          #plot(color_buffer$geometry, add = T)
        
        color_polygon <-
          color_polygon %>% 
          slice(-1)
        
    if(NROW(color_buffer) == 0 || color_buffer$area == 0){
        print("too small")
        area_left = F
        next()
    } 
    else {
      #from calc, there is enough space to draw a circle
      #polygon needs to be a string for distance calc to work
        color_line <-
          color_polygon_single %>% 
          st_cast("LINESTRING")
        #plot(color_line$geometry, add = F)
      #find centroid of buffered region        
        color_centroid <-
          color_buffer %>%
          st_point_on_surface()
  
        #plot(color_centroid$geometry, add = T)
      
      #get the distance of this point    
        color_dist <-
          st_distance(color_centroid[1,1], color_line)
        
      #create a circle of this size (color_dist)  
        color_circle <-
          color_centroid %>% 
          st_buffer(color_dist + .01)
        
        #plot(color_circle$geometry, add = T)
        
      #build dataset of circles
        color_circle_all <-
          rbind(color_circle, color_circle_all) %>%
          st_cast("MULTIPOLYGON")
          
        color_new <-
          color_polygon_single %>% 
          st_difference(st_union(st_buffer(color_circle, 0.8))) %>% 
          st_cast("POLYGON") %>% 
          mutate(area = st_area(.))
  
        #plot(color_new$geometry, add = F)
      if(NROW(color_new) == 0){
        print("nothing left")
        area_left = F
      }
      else {
        #add new polygon shape/shapes to the color_polygon table
          color_polygon <-
            rbind(color_new, color_polygon)  %>% 
            arrange(desc(area)) %>% 
            filter(area > area_allowed) %>% 
            st_difference(st_union(color_circle))

    
        print("conditions met")
        print(paste0(i, " - ",
                     j, " - ",
                     get_iteration, " - ",
                     NROW(color_polygon),
                     " left"))
  
    }
        #
    }
    #
    j = j+1
    get_iteration = get_iteration + 1
    next()
    }
  }
}
)

plot(color_circle_all$geometry, col = color_circle_all$hex2, border = NA, add = F)
```



# get representative colors
```{r}
get_mode <- 
  function(x) {
    ux <- unique(x)
    ux[which.max(tabulate(match(x, ux)))]
}

grid_base_points <- 
  grid_base %>%
  select(x, y, h, s, v, hex) %>% 
  st_as_sf(coords = c("x", "y")) %>% 
  st_buffer(modulo/2, nQuadSegs = 1)

#plot(grid_base_points$geometry)

color_circle_final <-
  color_circle_all %>% 
  mutate(ID = row_number()) %>% 
  st_join(grid_base_points, join = st_intersects)%>% 
  group_by(ID) %>% 
#  summarise(hex3 = get_mode(hex)) %>% 
#  ungroup()
 summarise(h = median(h),
            s = median(s),
            v = median(v)) %>% 
  ungroup() %>% 
  filter(!is.na(h)) %>% 
  mutate(hex3 = hsv(h, s, v))

color_circle_centroids <-
  color_circle_final %>%
  arrange(hex3) %>% 
  mutate(area = st_area(.),
         radius = sqrt(area)/pi) %>% 
  st_centroid() %>% 
  cbind(., st_coordinates(.)) %>% 
  st_set_geometry(NULL)


#plot(color_circle_all$geometry[1:20], col = "red", add = T)

plot(color_circle_final$geometry, 
     col = color_circle_final$hex3, border = NA)

ggplot() +
  geom_sf(data = color_circle_final, 
          aes(fill = hex3), 
          color = NA) +
  guides(fill = F)

st_write(color_circle_final, "kraken.shp")
write.csv(color_circle_centroids, "kraken_centroids.csv", row.names = F)

color_circle_centroids %>% 
  distinct(hex3) %>% 
  mutate(hex3 = paste0("<color>", hex3, "</color>"))


ggplot() +
  geom_point(data = color_circle_centroids,
             aes(x = X, y = Y, 
                 fill = hex3, 
                 size = pi*radius^2), 
             shape = 21, stroke = .5) +
  scale_fill_identity(guide = "none") +
  scale_size(guide = "none", range = c(.1,70)) +
  coord_fixed() +
  theme_minimal()

ggsave(filename="myPlot.pdf")

#get new colors
#  new_colors <-
#    color_circle_final %>% 
#    left_join(select(grid_base_points, -geometry))

#drops points
  #get coordinates of orig colors
  
  #get new colors
#  new_colors <-
#    grid_base_points %>% 
#   select(h, s, v) %>% 
#    aggregate(color_circle_all, mean) %>% 
#    mutate(hex3 = hsv(h, s, v))
  
#  plot(new_colors$geometry, col = new_colors$hex3)
```













### OLD METHOD -- grid of dots #######################
#Create 4 grids 
smallest size - x2 - x4 - x8
```{r}
build_box <-
  function(min_x, min_y, max_x, max_y){
  st_polygon(
    list(
      rbind(c(min_x, min_y),
            c(max_x, min_y),
            c(max_x, max_y), 
            c(min_x, max_y), 
            c(min_x, min_y))
      )
  )
}

grid_bounding_box <-
  build_box(min_x = min(grid_base$x), 
            min_y = min(grid_base$y), 
            max_x = max(grid_base$x), 
            max_y = max(grid_base$y))
  
grid_start <-
  grid_base %>% 
  st_as_sf(coords = c("x", "y")) %>% 
  select(hex, h2, s2, v2, hex2) %>% 
  st_buffer(dist = modulo * 0.3, nQuadSegs = 4) %>% 
  filter(lengths(st_within(., grid_bounding_box)) > 0) %>% 
  mutate(size = "mod/2",
         n_colors = 1,
         order = row_number())

plot(grid_start$geometry[1], col = grid_start$hex, border = NA)
```

```{r}
build_grid <-
  function(buffer_size, color_filter){
    #buffer_size = 4
    #create a base table
      base_table <-
        grid_start %>% 
        st_buffer(dist = modulo * buffer_size, nQuadSegs = 4) %>% 
        filter(lengths(st_within(., grid_bounding_box)) > 0) %>% 
        mutate(size = paste0("mod", modulo, "x", buffer_size)) #%>% 
        #mutate(n_points = colSums(st_intersects(grid_sf_1x, ., sparse = F)))

    #get # of colors within
      n_colors <-
        aggregate(grid_start["hex2"], base_table, FUN = n_distinct) %>% 
        rename(n_colors = hex2)

      sd_colors <-
        aggregate(grid_start["h2"], base_table, FUN = sd) %>% 
        rename(sd_colors = h2)
            
      mean_h <-
        aggregate(grid_start["h2"], base_table, FUN = mean) %>% 
        rename(mean_h = h2)

      mean_s <-
        aggregate(x = grid_start["s2"], base_table, FUN = mean) %>% 
        rename(mean_s = s2)
      
      mean_v <-
        aggregate(x = grid_start["v2"], base_table, FUN = mean) %>% 
        rename(mean_v = v2)


    #convert to data.frame
      st_geometry(n_colors) <- NULL
      st_geometry(sd_colors) <- NULL
      st_geometry(mean_h) <- NULL
      st_geometry(mean_s) <- NULL
      st_geometry(mean_v) <- NULL

    #append
      base_table$n_colors <- n_colors$n_colors
      base_table$sd_colors <- sd_colors$sd_colors
      base_table$mean_h <- mean_h$mean_h
      base_table$mean_s <- mean_s$mean_s
      base_table$mean_v <- mean_v$mean_v
      base_table$hex3 <- hsv(base_table$mean_h, 
                             base_table$mean_s, 
                             base_table$mean_v)
    
    #filter
      return(base_table %>% filter(n_colors <= color_filter))
  }

```

```{r}
add_to_grid <-
  function(sf_data){
    for(i in 1:nrow(sf_data)){
        if(lengths(st_intersects(sf_data[i,], new_grid, sparse = T)) == 0){
            new_grid <<- rbind(new_grid, sf_data[i,])
        }
      print(i)
    }
  }

plot_new_grid <-
  function(color_by){
    plot(new_grid$geometry, col = color_by, border = "grey30")
  }
```


```{r}  
#create largest circles
  grid_xl <- 
    build_grid(3, 3)
  
  plot(grid_xl$geometry[1])
  
  new_grid <- grid_xl[1,]
  add_to_grid(grid_xl) #48
  
  plot_new_grid(new_grid$hex)

#plot larges
  grid_lg <- 
    build_grid(2, 3) %>% 
    filter(lengths(st_overlaps(., new_grid)) == 0)
  
  add_to_grid(grid_lg)
  plot_new_grid(new_grid$hex)

#plot modulo
  grid_modsize <- 
    build_grid(1.5, 3) %>% 
    filter(lengths(st_overlaps(., new_grid)) == 0)
  
  add_to_grid(grid_modsize)
  plot_new_grid(new_grid$hex)

#plot mediums
  grid_med <- 
    build_grid(1.25, 3) %>% 
    filter(lengths(st_overlaps(., new_grid)) == 0)
  
  add_to_grid(grid_med)
  plot_new_grid(new_grid$hex)
  
#plot smalls
  grid_sm <- 
    build_grid(1, 3) %>% 
    filter(lengths(st_overlaps(., new_grid)) == 0)

  add_to_grid(grid_sm)
  plot_new_grid(new_grid$hex)

#plot x-smalls
  grid_xs <- 
    build_grid(1/12, 3) %>% 
    filter(lengths(st_overlaps(., new_grid)) == 0)

  add_to_grid(grid_sm)
  plot_new_grid(new_grid$hex)
  
  
  
final_grid <-
  rbind(
    new_grid,
    grid_start %>% 
        mutate(mean_h = h2,
               mean_s = s2,
               mean_v = v2,
               hex3 = hex2,
               sd_colors = 0.0) %>% 
          st_buffer(dist = 1) %>% 
          #filter(lengths(st_within(., new_grid)) == 0) #%>% 
          filter(lengths(st_intersects(., new_grid)) == 0) #%>% 
          #filter(lengths(st_touches(., new_grid)) == 0)
  ) #%>% st_buffer(dist = -.25)

plot(final_grid$geometry, 
     add = F, 
     #col = final_grid$size,
     col = final_grid$hex2
     #border = "grey40"
     )

left_join(
  
  grid_start[1:10,] %>% 
    select(order, geometry) %>% 
    unnest(geometry) %>% 
    st_coordinates()
  
  
  final_grid, st_coordinates(final_grid)) %>% 
ggplot(aes(X,Y, color = size)) +
  geom_point() +
  scale_color_identity()


#plot(new_grid$geometry%>% st_buffer(dist = -.25),
#     add = T, 
#     col = new_grid$hex3, border = NA)

table(final_grid$size)
```


#Crop each grid to image
```{r}

```

#place large circles first then remove points contained within large circles

*for x8 find first placement then skip every 8
  +check to see if color is representative of image: max out SL in HSL, get range of middle 75 H values 
  +check for overlap with any currently placed circles
```{r}

```




#From vignette
```{r}
nc <- st_read(system.file("shape/nc.shp", package="sf"))
plot(nc[1])
plot(nc[1,1], col = 'grey', add = TRUE)


```




########### not using #######################
  
```{r}  
 aggregate(x = grid_sf_1x["hex2"],
           by = grid_sf_8x,
           FUN = n_distinct)


colSums(st_intersects(grid_sf_1x, 
                      grid_sf_8x,
                      sparse = FALSE))

aggregate(x = grid_sf_1x["hex2"], 
          by = grid_sf_8x, 
          FUN = n_distinct)
[,1]


  st_within(grid_sf_1x[1:100,], grid_sf_8x[1,], sparse =  F)
  
  a <- 
    
  
  aggregate(nc[,"frac74"], 
          list(Ashe_nb = lengths(st_intersects(nc, Ashe)) > 0), mean))  

  aggregate(grid_sf_1x[,"hex2"], 
          list(new = lengths(st_intersects(grid_sf_1x, grid_sf_8x)) > 0), n_distinct)  


  sum(st_within(grid_sf_1x[1:100,], grid_sf_8x[1,], sparse = F))
    
result_private <- st_within(point_private_sf, world_sf, sparse = FALSE)  

### Calculate the total count of each polygon
# Store the result as ew columns "Count_all" and "Count_private" in world_sf
world_sf <- world_sf %>%
  mutate(Count_all = apply(result_all, 2, sum),
         Count_private = apply(result_private, 2, sum)) %>%
  # Calculate the percentage
  mutate(Percent = ifelse(Count_all == 0, Count_all, Count_private/Count_all * 100))



  mutate(pct_hue = sd(h))

```




#create shapes (svg layers)
*the ```polygonizer``` function requires [osgeo4w](https://trac.osgeo.org/osgeo4w/) 64-bit to be installed
```{r}
#raster
#read image
 image_initial <-
    raster("starrynight.png", band = 3) %>% 
    aggregate(fact = 17)
%>% 
    #rasterToPoints()
    #readPNG("starrynight.png") %>% 
    as.raster()

plot(image_initial)
    
    %>% 
    aggregate(image_initial, fact = 17)
      

plot(image_initial)
image_ratio <- nrow(image_initial) / ncol(image_initial) # image ratio
plot(c(0,1), c(0,image_ratio), type = "n", xlab = "", ylab = "", asp=1)
rasterImage(image_initial, 0, 0, 1, image_ratio) 

#convert to polygons

#get polygonizer function
  source("https://gist.githubusercontent.com/johnbaums/26e8091f082f2b3dd279/raw/7a8caa444fe63f0705fdb0d31239f1b202b6cb51/polygonizer.R")

  image_polygon <-
    polygonizer(image_initial, 
                outshape = "starrynight.shp", 
                pypath = (cmd = "C:/OSGeo4W64/OSGeo4W.bat"))
  
  spplot(image_polygon, col.regions=rainbow(200))


  rasterToPolygons(x, fun=NULL, n=4, na.rm=TRUE, digits=12, dissolve=FALSE)
```

```{r}
#svglite
a <- 
  svglite("starrynight_12.svg")
```


```{r}
  #filter(lengths(st_intersects(., y = grid_sf_8x[1, ], sparse = T)) == 0) %>% 
  #filter(lengths(st_within(., y = grid_sf_8x, sparse = T)) == 0) %>% 
  #filter(lengths(st_within(., y = grid_sf_4x, sparse = T)) == 0)


#%>% st_join(grid_bounding_box, join = st_within)


```

