---
format: 
  html:
    page-layout: custom
    fontsize: "12.5px"
execute:
  echo: false
  message: false
  warning: false
urlcolor: "#337ab7"
linkcolor: "#337ab7"
---

<!-- 
  to save as PDF: 
    - knit html
    - open in Chrome
    - view > print > save as PDF
      Scale: 85%
      Margins: custom
-->

```{css style}
table, .table, h3, .h3, h4, .h4 {
  margin-top: 0.5rem;
  margin-bottom: 0rem;
}

h1 {
  font-size: 3.6rem;
  color: black;
  margin-top: 1rem;
  margin-bottom: 0rem;
}

h2 {
  margin-top: 1rem;
  margin-bottom: 0rem;
}

p {
  margin-top: 0rem;
  margin-bottom: 0rem;
}

.sidebar {
  /*color: #555555;*/
  background-color: #f5f5f5;
  padding-top: 0px;
  padding-left: 10px;
  padding-right: 10px;
}
```

```{r workspace}
library(gt)
library(htmltools)
library(glue)
library(tidyverse)
library(shiny)
library(simplecolors)
library(fontawesome)
```

```{r colors-functions}
colors <-
  list(
    dark_grey = sc("grey5"),
    grey = sc("grey4"),
    light_grey = "#888888"
  )

section_subheader <- function(title, subtitle, when, where) {
  glue(
    '<p style = "text-align:left; font-size:1.1em;"> 
      {left} {right}
      <br> {bottom_left}{bottom_right}
    </p>',
    left = glue("<strong> {title} </strong>"),
    right = glue('<span style="float:right; font-size:1em;"> <i>{when}</i></span>'),
    bottom_left = glue('<span style="font-variant:small-caps; font-size:1em;">, {subtitle} </span>'),
    bottom_right = glue('<span style="float:right; font-size:1em;"> <i>{where}</i></span>')
  ) |> 
    HTML()
}
```


# Jake **Riley**
Senior Data Analyst  |  Philadelphia, PA |
[rjake@sas.upenn.edu](mailto:rjake@sas.upenn.edu) | `r fa('github')` [rjake](https://github.com/rjake)

<br>

::: {.grid}
::: {.g-col-4 .sidebar}

## `r fa(name = "rocket")` Goals
improving the performance of analytics teams - reducing technical debt - providing mentorship to junior analysts - building robust dashboards and reports

<br>

## `r fa("cogs")` Skills
**advanced**  
*data wrangling - data viz - R package development - code review*

**proficient**  
*SQL - Tableau - Qlik Sense - dbt - GitHub - GIS - Microsoft Office*

**familiar**  
*REST APIs - sentiment analysis - statistics*

**interested**  
*Python - Machine Learning - NLP*

<br>

## `r fa("laptop-code")` R Packages
[**headliner**](https://rjake.github.io/headliner) *(author)*  
*dynamic text for dasboards and reports*

[**shinyobjects**](https://rjake.github.io/shinyobjects/index.html) *(author)*  
*debug reactive objects at the console*

[**simplecolors**](https://rjake.github.io/simplecolors/articles/intro.html) *(author)*  
*intuitive color names*

[**whereiation**](https://rjake.github.io/whereiation/) *(author)*  
*automated exploratory data analysis*

<br>

## `r fa("users")` Community

*Code for Philly - DC Trans Coalition - Emergence Community Arts Collective - MakeoverMonday - Men’s Resource Center - Neighborhood Bike Works - OneDC - Project HOME - R-Ladies - TransHealth Conference*

:::

::: {.g-col-8}
## `r fa("briefcase")` Relevant Work Experience
*Only lists data-related jobs. Other work includes direct service in the field of HIV case management, internships, and retail.*

<br>

```{r CHOP}
section_subheader(
  title = "Clinical Data Programmer / Analyst III",
  subtitle = "Children's Hospital of Philadelphia",
  when = "2017 - Present",
  where = "Philadelphia, PA"
)
```
* Centrally support analytics team to identify and promote the best practices
* Enhance in-house data solutions via R packages, dashboard templates and dbt macros
* Author of over 30 dashboards, hundreds of data requests, and domain-specific data infrastructure
* Design novel datasets for the CHOP data warehouse (ex. diagnosis hierarchy)
* Identify assets that are underutilized or computationally expensive
* Increase PR utilization and code review. We started at 17% engagement and now at 73% (56 / 76 analysts)

```{r Comcast}
section_subheader(
  title = "BI Analyst - Human Resources",
  subtitle = "Comcast",
  when = "2016 - 2017",
  where = "Philadelphia, PA"
)
```

* Built HR dashboards for employee turnover, diversity, and data dictionary (~1K users)
* Automated quarterly reports for the senior vice president
* Used techniques such as travelling salesman algorithms to optimize travel for HR trainings

```{r Policy-Map}
section_subheader(
  title = "Data Analyst",
  subtitle = "PolicyMap",
  when = "2015 - 2016",
  where = "Philadelphia, PA"
)
```
* Aggregated over 150 national datasets across 9 geographies
* Introduced new automated process for testing and data validation

```{r WFM}
section_subheader(
  title = "Production Analyst",
  subtitle = "Whole Foods Market",
  when = "2003 - 2008",
  where = "Landover, MD"
)
```
* Automated the production schedule for the Mid-Atlantic commissary, supporting 32 stores
* Determined how many 180-gallon kettles of soup to be made each hour
* Minimized redundant usage of kitchen equipment in food preparation

<br>

## `r fa("university")`  Education

```{r}
section_subheader(
  title = "University of Pennsylvania",
  subtitle = "B.A. Sociology - Quantitative Methods  |  summa cum laude  |  phi beta kappa",
  when = "2015",
  where = ""
)
```
Non-traditional student. Coursework focused on GIS and data visualization

```{r}
section_subheader(
  title = "Community College of Philadelphia",
  subtitle = "A.A. Liberal Arts | with highest honors | phi theta kappa",
  when = "2012",
  where = ""
)
```

:::

:::
