---
format: 
  html:
    page-layout: article
    fontsize: "13px"
execute:
  echo: false
  message: false
  warning: false
urlcolor:  "steelblue"
linkcolor: "steelblue"
---

<!-- 
  to save as PDF: 
    - knit html
    - open in Chrome
    - view > print > save as PDF
      Scale: 85%
      Margins: custom
-->

```{css style}
/*
body { 
  min-width: 900px; 
  text-align: left;
}

#wrapper {
  width: 900px; 
  margin: 0 auto; 
  text-align: left; 
}
*/

body {
  color: #333333;
  font-family: Calibri;
}

img, svg {
  fill: darkslategrey;
}

table, .table, h3, .h3, h4, .h4 {
  margin-top: 0.5rem;
  margin-bottom: 0rem;
}

h1 {
  font-size: 3.6rem;
  color: darkslategray;
  margin-top: 0rem;
  margin-bottom: 0rem;
}

h2 {
  color: darkslategray;
  margin-top: 0.5rem;
  margin-bottom: 0rem;
}

p {
  margin-top: 0rem;
  margin-bottom: 0rem;
}

.sidebar {
  background-color: #f5f5f5;
  color: darkslategrey;
  padding-top: 0px;
  padding-left: 5px;
  padding-right: 10px;
}
```

```{r workspace}
library(gt)
library(htmltools)
library(glue)
library(tidyverse)
library(shiny)
library(simplecolors)
library(fontawesome)
```

```{r functions}
section_subheader <- function(title, subtitle, when, where) {
  glue(
    '<p style = "text-align:left; font-size:1.1em;"> 
      {left} {right}
      <br> {bottom_left}{bottom_right}
    </p>',
    left = glue("<strong> {title} </strong>"),
    right = glue('<span style="float:right; font-size:1em;"> <i>{when}</i></span>'),
    bottom_left = glue('<span style="font-variant:small-caps; font-size:0.9em;">{subtitle} </span>'),
    bottom_right = glue('<span style="float:right; font-size:0.9em;"> <i>{where}</i></span>')
  ) |> 
    HTML()
}

```

```{r, eval=FALSE}
tibble(
  left = "Jake **Riley**",
  right = 
    glue(
      "Senior Data Analyst <br>
      [rjake@sas.upenn.edu](mailto:rjake@sas.upenn.edu)<br>
      {fa('github')} [github.com/rjake](https://github.com/rjake)"
    )
  ) |> 
  gt() |> 
  fmt_markdown(columns = everything()) |> 
 tab_style( # column 1
    style = list(cell_text(align = "left", size = px(50))),
    locations = cells_body(columns = 1)
  ) |>
  tab_style( # column 2
    style = list(cell_text(align = "right")),
    locations = cells_body(columns = 2)
  ) |> 
  tab_options(
    table.width = pct(99),
    table.border.top.style = "hidden",
    table.border.bottom.style = "hidden",
    table.font.size = px(11),
    #table.font.color = colors$grey,
    #table.margin.left = "7px",
    column_labels.hidden = TRUE,
    container.overflow.x = FALSE,
    container.overflow.y = FALSE,
    table_body.hlines.color = "white",
    data_row.padding = px(1)
  )
```

<!-- 
<h1>
<span style="color:#333333;"> Jake </span> 
 <span style="color:darkslategrey;"> **Riley** </span>
</h1> 
-->



::: {.grid}
::: {.g-col-4 .sidebar}

# Jake **Riley**

<div style="color:darkslategrey;">
`r fa('envelope')` [rjake@sas.upenn.edu](mailto:rjake@sas.upenn.edu)  
`r fa('github')` [rjake](https://github.com/rjake) | 
`r fa("images")` [Portfolio](https://rjake.github.io/one-off-projects/)
</div>

<br> 

## `r fa(name = "rocket")` Goals {.sidebar}
improving the performance of analytics teams - reducing technical debt through mentorship and code review - building robust dashboards and reports

<br>

## `r fa("cogs")` Skills {.sidebar}
**advanced**  
*data wrangling - data viz - R package development - code review*

**proficient**  
*SQL - Tableau - Qlik Sense - dbt - GitHub - GIS - Microsoft Office*

**familiar**  
*REST APIs - sentiment analysis - statistics - Power BI*

**interested**  
*Python - Machine Learning - NLP*

<br>

## `r fa("laptop-code")` R Packages {.sidebar}
[**headliner**](https://rjake.github.io/headliner) *(author)*  
*dynamic text for dasboards and reports*

[**shinyobjects**](https://rjake.github.io/shinyobjects/index.html) *(author)*  
*debug reactive objects at the console*

[**simplecolors**](https://rjake.github.io/simplecolors/articles/intro.html) *(author)*  
*intuitive color names*

[**whereiation**](https://rjake.github.io/whereiation/) *(author)*  
*automated exploratory data analysis*

<br>

## `r fa("users")` Community {.sidebar}

*Code for Philly - DC Trans Coalition - Emergence Community Arts Collective - MakeoverMonday - Men’s Resource Center - Neighborhood Bike Works - OneDC - Project HOME - R-Ladies - TransHealth Conference*

:::

::: {.g-col-8}

<br>

## `r fa("briefcase")` Relevant Work Experience
*Only lists data-related jobs. Other work includes direct service in the field of HIV case management, internships, and retail.*

<br>

```{r CHOP}
section_subheader(
  title = "Clinical Data Programmer Analyst III",
  subtitle = "Children's Hospital of Philadelphia",
  when = "2017 - Present",
  where = "Philadelphia, PA"
)
```

* Innovate and enhance data solutions via R package development, dashboard templates, dbt macros
* Author of over 30 dashboards, hundreds of data requests, robust data marts
* Mentor junior analysts on analytic strategy, data visualization, technical solutions
* Teach deep-dive sessions regarding efficient SQL code, regular expressions, writing functions
* Design novel datasets for the CHOP Data Warehouse (ex. diagnosis hierarchy)
* Identify scheduled queries that are underutilized or computationally expensive
* Increase team utilization of GitHub and code review from 17% engagement to 73% (56 / 76 analysts)

```{r Comcast}
section_subheader(
  title = "BI Analyst - Human Resources",
  subtitle = "Comcast",
  when = "2016 - 2017",
  where = "Philadelphia, PA"
)
```

* Built HR dashboards in Tableau on employee turnover and diversity (~1K users)
* Automated quarterly reports for the senior vice president
* Participated in cross-department data viz working group
* Used travelling salesman and GIS methods to optimize travel for HR trainings

```{r Policy-Map}
section_subheader(
  title = "Data Analyst",
  subtitle = "PolicyMap",
  when = "2015 - 2016",
  where = "Philadelphia, PA"
)
```

* Aggregated over 150 national GIS datasets across 9 geographies in SQL Server 
* Introduced new automated process in R for testing and validating GIS results

```{r WFM}
section_subheader(
  title = "Production Planning Analyst",
  subtitle = "Whole Foods Market",
  when = "2003 - 2008",
  where = "Landover, MD"
)
```

* Automated production schedule for regional commissary, supporting 32 stores
* Predicted ingredient quantity required for joint fall and winter holidays
* Minimized food waste and redundant usage of kitchen equipment
* Created algorithms for weekly soup production schedule (~5K gallons a day)
* Created VBA macros in Excel for data collection and reporting

<br>

## `r fa("university")`  Education

```{r}
section_subheader(
  title = "University of Pennsylvania",
  subtitle = "B.A. Sociology - Quantitative Methods  |  summa cum laude  |  phi beta kappa",
  when = "2015",
  where = ""
)
```
Non-traditional student. Coursework focused on GIS and data visualization

```{r}
section_subheader(
  title = "Community College of Philadelphia",
  subtitle = "A.A. Liberal Arts | with highest honors | phi theta kappa",
  when = "2012",
  where = ""
)
```
:::
:::
