---
title: "Find Datasets"
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source_code: embed
    theme: lumen
    navbar:
    - icon: fa-github
      href: https://github.com/rjake/one-off-projects/blob/main/R/find-good-datasets
      align: right
resource_files:
- ds_list.Rds
- data_details.csv
---

```{r input-demo, eval=interactive()}
# https://rjake.shinyapps.io/Find-Good-Data/

library(shiny)
library(shinyobjects)
shiny::reactiveConsole(TRUE)

input <-
  list(
    # from JS
    arrow_left = TRUE,
    arrow_right = TRUE,
    # from widgets
    back = TRUE,
    forward = TRUE,
    pkg = "carData",
    col_types = c("discrete", "date"),
    selected = "carData::Arrests"
  )

```

```{css css-style}
.section.sidebar {
  overflow-x: hidden;
  overflow-y: scroll;
}

.bttn-gradient.bttn-primary, .bttn-simple.bttn-primary {
  background: #999;
}

.btn {
  text-transform: initial;
}
```

```{r workspace}
library(flexdashboard)
library(datasets)
library(tidyverse)
library(shinyWidgets)
library(reactable)
library(glue)
library(skimr)

options(width = 100) # for renderPrint -> verbatimTextOutput


# * ds_obj ----
ds_obj <- read_rds("ds_list.Rds")

# * ds_info ----
ds_info <- 
  read_csv("data_details.csv") |> 
  arrange(
    desc(pkg == "datasets"),
    pkg,
    name
  )

# * starting_data ----
# starting_data <- 
#   list(
#     pkg = "datasets",
#     available = ds_info$pkg_data[ds_info$pkg == "datasets"],
#     selected = "CO2"
#   )

```


```{js js-code}
// https://stackoverflow.com/questions/56600232/detecting-arrow-key-cursor-key-in-shiny

$(document).on('keydown', function(event){
    var key = event.which;
    if(key === 37){
        Shiny.setInputValue('arrow_left', true, {priority: 'event'});
    } else if(key === 39){
      Shiny.setInputValue('arrow_right', true, {priority: 'event'});
    }
});
```


```{r custom-fns}
display <- function(x) {
  set_names(
    x = x,
    nm = str_remove(x, ".*:")
  )
}

log_rv <- function() {
  cat(
    # "id = ", rv$id,
    # "\n choices = ", head(rv$available),
    # "\n selected = ", rv$data,
    "\n pkg = ", input$pkg,
    "\n type = ", input$type,
    "\n \n"
  )
}


iprint <- function(x, n = 15) {
  if (interactive()) {
    print(x, n = n)
  } else {
    return(x)
  }
}

vec_to_button <- function(inputId, vec, label = NULL, ...) {
  x <- table(vec)
  
  choices <-
    set_names(
      x = names(x),
      nm = glue("{names(x)} ({x})")
    )
  
  radioGroupButtons( 
    inputId = inputId,
    label = label,
    ...,
    size = "xs",
    choices = 
      list(any = "any") |> 
      append(choices)
  )
}


arrow <- function(id, dir) {
  actionBttn(
    inputId = id,
    label = NULL,
    style = "simple",
    color = "primary",
    size = "xs",
    icon = icon(
      name = paste0("long-arrow-alt-", dir)#, style = "color:black;"
    )
  )
}


custom_DT <- function(data, ...) {
  DT::datatable(
    data,
    filter = "top",
    escape = FALSE,
    options =
      list(
        ...,
        dom = "Brti",
        deferRender = FALSE,
        scrollY = 350,
        scrollX = TRUE,
        fixedHeader = FALSE,
        pageLength = nrow(data),
        lengthChange = FALSE
      )
  )
}

```



Sidebar {.sidebar data-width=470}
=======================================

### {data-height=40}

```{r reactive-data}

# * listen_col_types( ) ----
listen_col_types <- reactive({
  if (is.null(input$col_types) | "any" %in% input$col_types) {
    ids <- seq_along(ds_info$category)
  } else {
    
    # assign default value of all being true
    has_disc <- has_dt <- has_num <- rep(TRUE, nrow(ds_info))
    
    # update if necessary
    if ("discrete" %in% input$col_types) {
      has_disc <- (ds_info$n_discrete > 0)  # 860
    }
    
    if ("numeric" %in% input$col_types) {
      has_num <- (ds_info$n_numeric > 0) # 1031
    }
    
    if ("date" %in% input$col_types) {
      has_dt <- (ds_info$n_date > 0) # 33
    }
    
    ids <- which(has_disc & has_dt & has_num)
  }
  
  # ds_info[ids, ]
  ids
})


# * listen_pkg( ) ----
listen_pkg <- reactive({
  if (input$pkg == "any") {
    seq_along(ds_info$pkg)
  } else {
    which(ds_info$pkg == input$pkg)
  } 
})


# * listen_possible( ) ----
listen_possible <- reactive({
  intersect(listen_pkg(), listen_col_types())
})
```

### {data-height=40}

```{r input-col_types}

checkboxGroupButtons(
  inputId = "col_types",
  label = "Column types include",
  checkIcon = list(yes = icon("check")),
  choices = c("any", "discrete", "numeric", "date"),
  selected = "discrete"
)

```


```{r input-pkg}
renderUI({
  pkgs <- ds_info$pkg[listen_col_types()]
  #selected <- pkgs[1]
  
  vec_to_button(
    inputId = "pkg",
    label = "Select a package",
    vec = pkgs#,selected = selected
  ) 
})

```


###
```{r input-arrows}
renderUI({
 glue(
   "Browse data sets ({n})",
   n = length(listen_possible())
  ) |> 
    h5()
  
})

shiny::fluidRow(
  arrow("back",    "left"),
  arrow("forward", "right"),
  a("or use arrow keys", style = "color:#999;"),
  style = "margin-left: 0px; margin-bottom: 10px"
)


observeEvent(list(input$back, input$arrow_left), {
  req(input$selected)
  id_names <- ds_info$pkg_data[listen_possible()]
  get_id <- which(id_names == input$selected)
  new_id <- max(get_id - 1, 1)

  updateRadioGroupButtons(
    session,
    inputId = "selected",
    size = "sm",
    selected = id_names[new_id]
  )
})

observeEvent(list(input$forward, input$arrow_right), {
  req(input$selected)

  id_names <- ds_info$pkg_data[listen_possible()]
  get_id <- which(id_names == input$selected)
  new_id <- min(get_id + 1, length(id_names))

  updateRadioGroupButtons(
    session,
    inputId = "selected",
    size = "sm",
    selected = id_names[new_id]
  )
})


```

```{r input-selected}

renderUI({
  req(input$pkg)
 # if (input$pkg != starting_data$pkg) {
    ids <- listen_possible()
    choices <- ds_info$pkg_data[ids]
    selected <- choices[1]
  # } else {
  #   choices <- starting_data$available
  #   selected <- starting_data$data
  # }
  
  
  radioGroupButtons(
    inputId = "selected",
    label = NULL,
    size = "xs",
    choices = display(choices),
    selected = selected
  )
})

```


Preview
=======================================

Column
---------------------------------------

### {data-height=60}
```{r data-info}

# TODO: add title: packageDescription("beeswarm")$Title

renderUI({
  #print(input$selected)
  ds_info |> 
    filter(pkg_data == input$selected) |>
    mutate(
      dim = replace_na(dim, ""),
      cat_addl = ifelse(class != category, glue(" ({category})"), ""),
      dim_addl = ifelse(is_df & is_trunc, " (truncated for display)", "")
    ) |> 
    glue::glue_data(
      "{strong(pkg_data)} - {title}\\
      <br/> {{{class}}}{cat_addl} {dim}{dim_addl}
      <br/>"
    ) |>
    paste(
      actionLink(
        inputId = "meta",
        label = "Metadata",
        style = "color:dodgerblue;",
        onclick = "location.href='#section-metadata';"
      ),
      "|",
      actionLink(
        inputId = "stats",
        label = "Stats"
      )
    ) |> 
    HTML()
})

output$skimr_results <- renderPrint(
  expr = {
    x <- ds_obj[[input$selected]]$data
    skimr::skim(x) |> 
      skimr::partition()
  }
)


 observeEvent(input$stats, {
   showModal(
     modalDialog(
       title = "Stats",
       verbatimTextOutput("skimr_results"),
       easyClose = TRUE,
       size = "l",
       footer = NULL
     )
    )
 })


```

### 

```{r output-table}
# https://stackoverflow.com/questions/41381466/can-we-either-print-or-plot-in-shiny-in-same-panel
renderReactable({
  x <- ds_obj[[input$selected]]$data
  reactable(x, filterable = TRUE, pagination = FALSE)
})

```


Metadata
=======================================     
   
Column
---------------------------------------

### {data-height=30}

```{r back-arrow}
actionButton(
  inputId = "back",
  label = "Back",
  icon = icon(name = "long-arrow-alt-left"),
  style = "color:dodgerblue;",
  onclick = "location.href='#section-preview';"
)

#p("This table is filtered by the selections on the left")
```

### 
```{r metadata, eval=!FALSE}

### 
#renderReactable({
  #ids <- listen_possible()
  
  ds_info |> 
    #slice(ids) |> 
    select(
      title,
      name, pkg, class,
      n_discrete, n_numeric, n_date,
      #dim,
      n_row, n_col
    ) |> 
    arrange(name) |> 
    mutate(across(where(is.character), as.factor)) |> 
    reactable::reactable(
      filterable = TRUE, pagination = FALSE,
      columns = list(
        title = colDef(width = 300, style = list(backgroundColor = "#f7f7f7")),
        name = colDef(width = 100, style = list(fontWeight = "bold"))
      )
    )
#})
```

About
=====================================     
   
Column
-------------------------------------

Hi. Thanks for visiting the app. I hope you found it useful. The goal was to create a way to preview built-in data sets that might be useful to use. The data sets come from base R, the tidyverse, and a few other packages. This work was inspired by the [`RPackages` project](https://vincentarelbundock.github.io/Rdatasets/articles/data.html) by Vincent Arel-Bundock.

I used some criteria to pare down the data sets that are included:

* data frames with at least 30 rows and 5 columns
* or data frames with at least one character/factor column


##### Presentation:
```{r}
specs <- ds_obj$`tidyr::billboard`$data |> dim()
```

* to make this a lighter sized app, the data sets are truncated to `r specs[1]` rows and a max of `r specs[2]` columns
* the data listed under `datsets` shows what comes with R on installation. You can find installed data from all packages using `data(package = .packages(all.available = TRUE))` (you can add `$results` to view it as a data frame)
* the button for `discrete` might seem misleading for factors that are represented as integers. For example the `Diet` column in the `ChickWeight` table is a factor of integers 1-4
* code for the app can be found via the `</>` icon in the top right and the underlying files are located on [my github](https://github.com/rjake/one-off-projects/blob/main/R/find-good-datasets)
* if you can think of packages that should be included, [shoot me an email](mailto:rjake@sas.upenn.edu)

##### Note:

Some packages like `AER` and `Stat2Data` have data that is only accessible via the `data()` function. For example, you won't find `SandwichAnts` via `Stat2Data::SandwichAnts`, you'll have to use `data("SandwichAnts", package = "Stat2Data")` and then it will appear in your global environment. 

